### 2017-11-10 Graduate - Introduction to Analysis I/Assignment 7/7-Homework20171108.tex
add prob 1

Necessity.
% Sufficiency. First, we show $\{I_k\}$ is a Vitali cover of $E$. Otherwise, there exists $x\in E, ~\epsilon > 0$, s.t. for each $I_k $ for which $x\in I_k $, $m(I_k) > \epsilon$. Then
% $$\sum_{k=1}^{\infty}m(I_k) \ge \sum_{x\in I_k}m(I_k) \ge \sum\limits_{x\in I_k}\epsilon = \infty
% $$
% since $x$ belongs to infinity many of $I_k $. This makes a contradiction with the assumptions.

% By Problem 6.6 we know Vitali Covering Lemma holds for general nondegenerate intervals, then

>>>>

Necessity. With the definition of outer measure, for each $\epsilon_n = \epsilon{1}{2^n} $, there exist an open set $O_n = \bigcup\limits_{j=1}^{\infty}I_{n_j} $ being the construction of open intervals, s.t. $E\subset O_n $, and $m(O_n) = \sum\limits_{j=1}^{\infty}m(I_{n_j}) < \epsilon_n $. Let $\{I_n\} = \{I_{n_j}\}_{n, j} $, then for each $x\in E$, $x$ belongs to infinitely many of these open intervals, and $\sum\limits_{n=1}^{\infty}m(I_n) = \epsilon < \infty$.
% Let $\mathcal{F} = \bigcup O_k $, where $O_k = \bigcup I_{k_j} $ is an open set covering $E$. Then since $E$ is a set of outer measure 0, for each $\epsilon > 0$, there exists $O_k $, s.t. $O_k \supset E $ and $m(O_k) < \epsilon$. Then for each $x\in E$, $x\in O_k \in \mathcal{F}$. This means $\mathcal{F}$ is a (general) Vitali cover of $E$. By Problem 6.6 (Gereral case of Vitali covering lemma), for $\epsilon_n = \frac{\epsilon}{2^n}$, there exists
